\spacesubsection
\section{Projects}

\cventry{\textsc{July 2015--Present}}{Media Protection System}{at Irdeto B.V}{}{}{
    Multi-tenant backend video protection system for VOD and Live content. Integrated with multiple media streaming technologies
    such as HLS, CENC/DASH and many DRM systems: PlayReady, Widevine, FairPlay Streaming, Adobe Primetime, inhouse system.
    \newline
    Extensively using functional programming techniques.
    }

\cvline{Responsibilities}{
    Important role in all aspects of product development: design, implementation and testing new features.
    Responsible for integration with streaming technologies and DRM systems.
    \newline
    Adopting functional programming for Java to deliver high quality product.
    \newline
    Key role in spreading knowladge within the team and building cross-functional team.
    \newline
    Participated in building CI infrastructure based on Jenkins and Docker.
    }

\cvline{Technologies}{Java 8, Scala, Hibernate via JPA, PostgreSQL, Kafka, Guice, Jersey, TestNG, Jetty, Maven, Docker}

\spacesubsection
\cventry{\textsc{November 2013--July 2015}}{Search \& Discovery}{at Irdeto B.V}{}{}{
    REST and Java API to search video metadata presented in the system, part of bigger OTT solution.
    Migration from C\# and SQL solution to Java and ElasticSearch}

\cvline{Responsibilities}{
    Design and development of scalable REST API on top of ElasticSearch for full text search.
    I started from proof of concept and it has resulted in fully functional solution, designed Search DSL.
    \newline
    Responsible for interaction with ElasticSearch (writing and optimizing search queries,
    correct document analysis, multilingual support), performance testing}

\cvline{Technologies}{Java 7/8, ElasticSearch, Spring, Jersey, Jetty, Maven, JUnit, Amazon EC2, BlazeMeter/JMeter}

\spacesubsection
\cventry{\textsc{2012--2013}}{Online photo album editor}{at Sibers}{}{}{
    Online photoalbum editor with server side rendering}

\cvline{Responsibilities}{
    Design and implementation of SaaS application, work on GDI+ image renderer.
    Single page application using Backbone.js, HTML5, CSS3, integration with Picasa/Google+ and Facebook}

\cvline{Technologies}{ASP.NET MVC 4/Web API, EF Code First, Backbone.js, Twitter Bootstrap,
    Google API, Facebook Graph API, HTML5, CSS3}

\spacesubsection
\cventry{\textsc{2011--2012}}{Medical system for self diagnostics}{at Sibers}{}{}{
    Medical system for self-diagnosis based on Orchard CMS.}

\cvline{Responsibilities}{
    Database design, implementation of Orchard CMS modules for the system, mobile web version
    based on jQuery Mobile, integration with Google API}

\cvline{Technologies}{Orchard CMS, Fluent NHibernate, WCF WebApi, iTextSharp, jQuery, jQuery Mobile,
    Google Maps, Google Analytics}


